R Notebook

### 2017-12-18 datasets/RNA-Seq/rna-seq-benchmarkFDR.Rmd
filter geneExp object to solve the weird hill dist

# comparison tools/functions
library(SummarizedBenchmark)
sourceDirectory("~/Downloads/benchmark-fdr/datasets/R/")

@@

```{r}
#Load expression data
load('~/Downloads/dsdObjects.RData')

@@

#Buid DESeq object and run DESeq2
dds <- DESeq(filteredDsd1, parallel = T)
res <- results(dds, independentFiltering = F)

#Build input data frame for summarized benchmark
#Important to not change col names since SB is strict about that
geneExp <- data.frame(geneName=rownames(res), pval=res$pvalue, SE=res$lfcSE, 
                      ind_covariate = res$baseMean, effect_size=res$log2FoldChange, test_statistic=res$stat)

@@

```{r}
strat_hist(geneExp, pvalue="pval", covariate="ind_covariate", maxy=10)
```

>>>>

# comparison tools/functions
library(SummarizedBenchmark)
sourceDirectory("~/Documents/Research/benchmark-fdr/datasets/R/")

@@

```{r}
#Load expression data
load('~/Documents/Research/benchmark-fdr/datasets/RNA-Seq/dsdObjects.RData')

@@

#Buid DESeq object and run DESeq2
dds <- DESeq(filteredDsd1, parallel = T) # This step can take a few minutes since we have many samples
res <- results(dds, independentFiltering = F)

#Build input data frame for summarized benchmark
#Important to not change col names since SB is strict about that
geneExp <- tbl_df(data.frame(geneName=rownames(res), pval=res$pvalue, SE=res$lfcSE, 
                      ind_covariate = res$baseMean, effect_size=res$log2FoldChange, test_statistic=res$stat))

geneExp <- geneExp %>% na.omit() %>% dplyr::filter(ind_covariate>=1)

@@

```{r}
strat_hist(geneExp, pvalue="pval", covariate="ind_covariate", maxy=25)
```
